Report

### 2022-05-13 Analysis/Report.Rmd
update 2022-05-13 19:29:25

```{r tabconf, echo = F, message=F}
tab <- read.csv("../confusion.csv", stringsAsFactors = FALSE)
names(tab)[1] <- "Metric"
tab$Metric <- gsub("^.+_", "", tab$Metric)
tab <- tab[!tab$Metric == "lr", !grepl("iu", names(tab))]
names(tab) <- gsub("_ic", "", names(tab))
names(tab)[match(names(rename), names(tab))] <- rename
tab <- tab[tab$Metric %in% c("sensitivity", "specificity", "accuracy"),]
rownames(tab) <- NULL
knitr::kable(tab, digits = 2, caption = "Marginal confusion matrix metrics.")
```
These results indicate that all algorithms except PBF had low sensitivity to detect a true effect.
In contrast, specificity was very high for all algorithms except PBF.
This suggests that the other algorithms classified most conditions as negatives (no effect found),
regardless of the existence of a population effect.
The PBF trades a loss of specificity for increased sensitivity,
and average levels of both were approximately equal.
As the PBF vastly outperformed other BFs, these were omitted from further analysis.

@@

```{r tabeffect, echo = FALSE}
tab <- read.csv("../effect_of_conditions.csv", stringsAsFactors = FALSE)
tab <- tab[, !grepl("(gpbf|tbf)", names(tab))]
tab <- tab[, c("condition", "prodbf_ic", "rma", "ipd", "allsig", "prodbf_ic.vs..rma", "ipd.vs..prodbf_ic", "allsig.vs..prodbf_ic")]
names(tab) <-  c("Factor", "PBF", "RMA", "IPD", "VC", "vs RMA", "vs IPD", "vs VC")

knitr::kable(tab, digits = 2, caption = "Partial eta squared of the effect of each design factor on accuracy for each algorithm and for the difference between PBF and all other algorithms (e.g., vs RMA).")
```
PBF performance was most impacted by sample size $n$, followed by the number of groups $k$, and residual heterogeneity.

@@

```{r fign, fig.cap="Mean performance by sample size"}
res <- readRDS("../confusion_by_cond.RData")
res <- res[res$alg %in% c("ipd", "rma", "allsig", "prodbf_ic"), ]

@@

```{r, fig.cap="Mean performance by errorsd"}

# dat <- readRDS(file.path("../Sim", "sim_results_2022-05-07.RData"))
# varsout <- c("ipd", "rma", "allsig", "prodbf_ic")
# varspred <- c("errorsd", "n", "k", "hyp_val")
# 
# df_plot <- dat[!es < .1,  lapply(.SD, function(var) {
#   as.vector(table(ordered(es > .1, levels = c("FALSE", "TRUE")), ordered(var > 3, levels = c("FALSE", "TRUE"))))
# }), .SDcols = varsout, by = "errorsd"]
# 
# tabres[, metric := rep(c("TN", "FN", "FP", "TP"), nrow(tabres)/4)]
# 
# tabres <- melt(tabres, measure.vars = varsout,
#              variable.name = "alg", value.name = "val")
# tabres <- dcast(tabres, errorsd + n + k + hyp_val + alg ~ metric, value.var = "val")
# tabres[, alpha := FP / (FP + TN)]
# tabres[, beta := FN / (TP + FN)]
# tabres[, sensitivity := 1-beta]
# tabres[, specificity := 1-alpha]
# tabres[, accuracy := (TP + TN) / (TP+TN+FP+FN)]

df_plot <- melt(res, measure.vars = c("sensitivity", "specificity"),
             variable.name = "Outcome", value.name = "val")
df_plot <- df_plot[ ,list(mean=mean(val)), by=c("errorsd", "Outcome", "alg")]
ggplot(df_plot, aes(x = errorsd, y = mean, group = interaction(Outcome, alg), shape = alg, linetype = Outcome)) +
  geom_point() +
  geom_line() +
  theme_bw() +
  labs(y = "Mean performance")
```

>>>>

```{r tabconf, echo = F, message=F}
tab <- read.csv("../confusion.csv", stringsAsFactors = FALSE)
names(tab)[1] <- "Metric"
tab$Metric <- gsub("^.+_", "", tab$Metric)
tab <- tab[!tab$Metric == "lr", !grepl("iu", names(tab))]
names(tab) <- gsub("_ic", "", names(tab))
# names(tab)[match(names(rename), names(tab))] <- rename
tab <- tab[tab$Metric %in% c("sensitivity", "specificity", "accuracy"),]
rownames(tab) <- NULL
knitr::kable(tab, digits = 2, caption = "Marginal confusion matrix metrics.")
```
These results indicate that all algorithms except PBF had low sensitivity to detect a true effect.
In contrast, specificity was very high for all algorithms except PBF.
This suggests that the other algorithms classified most conditions as negatives (no effect found),
regardless of the existence of a population effect.
The PBF trades a loss of specificity for increased sensitivity,
and average levels of both were approximately equal.
As the PBF vastly outperformed other BFs, these were omitted from further analysis.

@@

```{r tabeffect, echo = FALSE}
tab <- read.csv("../effect_of_conditions.csv", stringsAsFactors = FALSE)
tab <- tab[, !grepl("(gpbf|tbf)", names(tab))]
tab <- tab[, grepl("^\\w+$", names(tab)) | (grepl("\\.{2}", names(tab)) & grepl("PBF", names(tab)))]
names(tab)[grepl("\\.{2}", names(tab))] <- paste0("vs ", gsub("(\\.|PBF|vs)", "", names(tab)[grepl("\\.{2}", names(tab))]))
knitr::kable(tab, digits = 2, caption = "Partial eta squared of the effect of each design factor on accuracy for each algorithm and for the difference between PBF and all other algorithms (e.g., vs RMA).")
```
PBF performance was most impacted by sample size $n$, followed by the number of groups $k$, and residual heterogeneity.

@@

```{r fign, fig.cap="Mean performance by sample size"}
res <- readRDS("../confusion_by_cond.RData")
res <- res[res$alg %in% c("IPD", "RMA", "VC", "PBF"), ]

@@

```{r, fig.cap="Mean performance by errorsd"}
df_plot <- melt(res, measure.vars = c("sensitivity", "specificity"),
             variable.name = "Outcome", value.name = "val")
df_plot <- df_plot[ ,list(mean=mean(val)), by=c("reliability", "Outcome", "alg")]
ggplot(df_plot, aes(x = reliability, y = mean, group = interaction(Outcome, alg), shape = alg, linetype = Outcome)) +
  geom_point() +
  geom_line() +
  theme_bw() +
  labs(y = "Mean performance")
```
